\problemname{Joined Sessions}
Lucy is very lazy. Her boss asked her to go to a conference and of course
she wants her to go to as many meetings as possible. But Lucy is lazy and
so she decides to choose her meetings such that all other meetings overlap with
at least one of the meetings she is attending. This way, her boss cannot
complain as there is no way for her to attend additional meetings.

While reading the schedule of the conference, Lucy finds out that even with this
approach of choosing the meetings there are quite many meetings she has to attend.
Luckily, her good friend Max is one of the organisers of the conference and in
particular responsible for the timetable. Max is unfortunately not able to
cancel meetings or to reschedule them, but he can help Lucy in another way.

Since the meetings are normally boring, nobody will pay too much attention if the
topic changes. Therefore, whenever there are two meetings that overlap, he can combine
them into a single meeting instead. Two meetings $a$ and $b$ overlap if
$\text{start}(a) \le \text{start}(b) \le \text{end}(a)$ or vice versa, and when
they are combined the new meeting will start at time
$\min(\text{start}(a),\text{start}(b))$ and end at time
$\max(\text{end}(a),\text{end}(b))$. Max can then repeat this merging process
and it is even possible to further combine these combined meetings with other
meetings. Non-overlapping meetings cannot be combined as then people would notice
that someone is tampering with the schedule.

Lucy now wonders if she can reduce the number of meetings she has to attend
with this method. If it is possible, how many such merges are necessary to
reduce this number by at least one?

\section*{Input}
The input consists of:
\begin{itemize}
	\item One line with an integer $n$ ($2 \leq n \leq 10^6$), the number of
	meetings.
	\item $n$ lines describing the meetings, each with two integers $a$ and $b$ ($0 \leq a \leq b \leq
	10^9$), where $a$ is the start time and $b$ the end time of one of the given
		meetings.
\end{itemize}


\section*{Output}
If it is possible to reduce the number of meetings Lucy has to attend, then
output the minimum number of merging operations needed to do so. Otherwise output
\texttt{impossible}.
